---
title: "7 2SLS Regression"
author: "Andy Zack"
date: "`r Sys.Date()`"
format: html
self-contained: true
editor: source
---

## Load Packages

```{r load_packages}
#| message: false
library(tidyverse)
library(aws.s3)
library(kableExtra)
library(broom)
library(fixest)
library(marginaleffects)
```

## Other Setup

```{r other_setup}
Sys.setenv("AWS_ACCESS_KEY_ID" = Sys.getenv("TMC_s3_access_key"),
           "AWS_SECRET_ACCESS_KEY" = Sys.getenv("TMC_s3_secret_key"))

bucket = "tmc-research-projects"
```

## Load Data

```{r load_data}
clean_df <- s3read_using(
  FUN = read_rds,
  bucket = bucket,
  object = "p080_moveon_impact_analysis/clean_df.rds")
```

## Load ITT regressions results

```{r read_reg_results}
#| message: false
regression_results <- s3read_using(
  FUN = read_csv,
  bucket = bucket,
  object = "p080_moveon_impact_analysis/regression_results.csv"
)
```

## Run 2SLS Regression

```{r run_regression}
fit_2sls <- feols(
  voted_24 ~ 
    gender +
    age +
    target_geography_state +
    voted_22 +
    voted_20 +
    voted_p22 +
    voted_p20 +
    race +
    ts_tsmart_presidential_general_turnout_score +
    ts_tsmart_presidential_general_turnout_score_sq +
    ts_tsmart_partisan_score +
    ts_tsmart_partisan_score_sq +
    urbanicity +
    ts_tsmart_college_graduate_score |  
    # IV part: 
    exp_contacted ~ treat,
  data = clean_df)
```

## Print Regression Results

```{r print_regression_results}
tidy(fit_2sls) %>%
  kable()

fitstat(fit_2sls, "ivf")

ame_contacted <- avg_slopes(fit_2sls, variables = "exp_contacted", conf_level = .9)
preds <- avg_predictions(fit_2sls, variables = "exp_contacted", conf_level = .9)
r_squared <- r2(fit_2sls)['r2']
n_contacted <- sum(clean_df$exp_contacted)
n_not_contacted <- sum(clean_df$exp_contacted == 0)
  
ame_contacted_clean <- ame_contacted %>%
  tidy() %>%
  transmute(regression_type = "2SLS",
            condition = "contacted - not contacted",
            n = NA,
            predicted_prob = estimate,
            se = std.error,
            ci_low_90 = conf.low,
            ci_high_90 = conf.high,
            p_value = p.value,
            adj_rsq = r_squared)

preds_clean <- preds %>%
  tidy() %>%
  transmute(regression_type = "2SLS",
            condition = if_else(exp_contacted == 1, "contacted", "not contacted"),
            n = if_else(exp_contacted == 1, n_contacted, n_not_contacted),
            predicted_prob = estimate,
            se = std.error,
            ci_low_90 = conf.low,
            ci_high_90 = conf.high,
            p_value = p.value,
            adj_rsq = r_squared)

all_regression_results <- regression_results %>%
  filter(regression_type == "OLS") %>%
  bind_rows(ame_contacted_clean) %>%
  bind_rows(preds_clean)

kable(all_regression_results)
```

The F test is significant and above 10, which is good. That means that the IV setup is reasonable; The instrument strongly predicts contact and is not a weak instrument. Being contacted does not significantly increase turnout, though the best estimate is that it increases turnout by 1.4pp.

## Save Regression Results

```{r}
s3write_using(x = all_regression_results, 
              FUN = write_csv, 
              object = "p080_moveon_impact_analysis/regression_results.csv", 
              bucket = "tmc-research-projects")
```
